%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \pubentry
    {J. Chem. Inf. Model. 2023, 63, 1, 321–334} % Citation
    {High-Throughput Prediction of the Impact of Genetic Variability on Drug Sensitivity and Resistance Patterns for Clinically Relevant Epidermal Growth Factor Receptor Mutations from Atomistic Simulations} % Title
    {2023} % Year
    {} % Code
    {Aristarc Suriñach, Adam Hospital, Yvonne Westermaier, Luis Jordà, Sergi Orozco-Ruiz, Daniel Beltrán, Francesco Colizzi, Pau Andrio, Robert Soliva, \hlauthor{Martí Municoy}, Josep Lluís Gelpí, Modesto Orozco} % Author
    {} % Image
    {10.1021/acs.jcim.2c01344} % DOI

%---------------------------------------------------------
  \pubentry
    {J. Biol. Chem. (2023) 299(6) 104794} % Citation
    {Selective inhibitors of the PSEN1–gamma-secretase complex} % Title
    {2023} % Year
    {} % Code
    {Lutgarde Serneels, Rajeshwar Narlawar, Laura Perez-Benito, \hlauthor{Martí Municoy}, Victor Guallar, Dries T’Syen, Maarten Dewilde, François Bischoff, Erwin Fraiponts, Gary Tresadern, Peter W. M. Roevens, Harrie J. M. Gijsen, Bart De Strooper} % Author
    {} % Image
    {10.1016/j.jbc.2023.104794} % DOI

%---------------------------------------------------------
  \pubentry
    {WIREs Comput Mol Sci. 2022;e1653} % Citation
    {Combining machine-learning and molecular-modeling methods for drug-target affinity predictions} % Title
    {2022} % Year
    {} % Code
    {Carles Perez-Lopez, Alexis Molina, Estrella Lozoya, Victor Segarra, \hlauthor{Martí Municoy}, Victor Guallar} % Author
    {} % Image
    {10.1002/wcms.1653} % DOI

%---------------------------------------------------------
  \pubentry
    {WIREs Comput Mol Sci. 2022;e1622} % Citation
    {Pre-exascale HPC approaches for molecular dynamics simulations. Covid-19 research: A use case} % Title
    {2022} % Year
    {} % Code
    {Miłosz Wieczór, Vito Genna, Juan Aranda, Rosa M. Badia, Josep Lluís Gelpí, Vytautas Gapsys, Bert L. de Groot, Erik Lindahl, \hlauthor{Martí Municoy}, Adam Hospital, Modesto Orozco} % Author
    {} % Image
    {10.1002/wcms.1622} % DOI

%---------------------------------------------------------
  \pubentry
    {J. Chem. Theory Comput. 2020, 16, 12, 7655–7670} % Citation
    {aquaPELE: A Monte Carlo-Based Algorithm to Sample the Effects of Buried Water Molecules in Proteins} % Title
    {2020} % Year
    {} % Code
    {\hlauthor{Martí Municoy}, Sergi Roda, Daniel Soler, Alberto Soutullo, Victor Guallar} % Author
    {} % Image
    {10.1021/acs.jctc.0c00925} % DOI

%---------------------------------------------------------
  \pubentry
    {ACS Catal. 2020, 10, 22, 13584–13595} % Citation
    {Fatty-Acid Oxygenation by Fungal Peroxygenases: From Computational Simulations to Preparative Regio- and Stereoselective Epoxidation} % Title
    {2020} % Year
    {} % Code
    {\hlauthor{Martí Municoy}, Alejandro González-Benjumea, Juan Carro, Carmen Aranda, Dolores Linde, Chantal Renau-Mínguez, René Ullrich, Martin Hofrichter, Victor Guallar, Ana Gutiérrez, Angel T. Martínez} % Author
    {} % Image
    {10.1021/acscatal.0c03165} % DOI

%---------------------------------------------------------
  \pubentry
    {J. Chem. Theory Comput. 15, 6243−6253} % Citation
    {PELE-MSM: A Monte Carlo Based Protocol for the Estimation of Absolute Binding Free Energies} % Title
    {2019} % Year
    {NostrumBioDiscovery/msm\_pele} % Code
    {Joan F. Gilabert, Christoph Grebner, Daniel Soler, Daniel Lecina, \hlauthor{Martí Municoy}, Oriol Gracia Carmona, Robert Soliva, Martin J. Packer, Samantha J. Hughes, Christian Tyrchan, Anders Hogner, Victor Guallar} % Author
    {} % Image
    {10.1021/acs.jctc.9b00753} % DOI

%---------------------------------------------------------
  \pubentry
    {Catal. Sci. Technol. 9, 1398–1405} % Citation
    {Selective synthesis of 4-hydroxyisophorone and 4-ketoisophorone by fungal peroxygenases} % Title
    {2019} % Year
    {} % Code
    {Carmen Aranda, \hlauthor{Martí Municoy}, Víctor Guallar, Jan Kiebist, Katrin Scheibner, René Ullrich, José C. del Río, Martin Hofrichter,
Angel T. Martínez, Ana Gutiérrez} % Author
    {} % Image
    {10.1039/c8cy02114g} % DOI

%---------------------------------------------------------
  \pubentry
    {J. Comput. Chem. 38 (24), 2118-2126} % Citation
    {GaudiMM: A modular multi-objective platform for molecular modeling} % Title
    {2017} % Year
    {insilichem/gaudi} % Code
    {Jaime Rodríguez-Guerra, Giuseppe Sciortino, Jordi Guasp, \hlauthor{Martí Municoy}, Jean-Didier Maréchal} % Author
    {} % Image
    {10.1002/jcc.24847} % DOI

%---------------------------------------------------------
\end{cventries}
